%Copyright 2013 Stephen Kraemer

\documentclass{letter}

\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\usepackage{grffile}
\usepackage{geometry}
\usepackage{enumitem}

%margins
\newgeometry{left=20mm,right=20mm,top=20mm, bottom=20mm}

%get rid of headers/footers (i.e. no page numbers)
\pagestyle{empty}

%Get rid of space before beginning of list
\setlist{nolistsep}

\begin{document}

{\Huge\bf Stephen Kraemer} \hfill
\begin{tabular}{r}
  \href{https://github.com/straemer}{github.com/straemer} \\
  (226) 606-4052 \\
  \href{mailto:sbkraeme@uwaterloo.ca}{sbkraeme@uwaterloo.ca}
\end{tabular}

%horizontal line
\vskip 2pt
\hrule

{\large\bf SUMMARY OF QUALIFICATIONS}

\begin{itemize}
  \item Expert C/C++ programmer, familiar with python, RobotC, Java, C\#, and Matlab.
  \item Embedded systems: Arduino, Lego Mindstorms, Raspberry Pi.
  \item Proficient GNU/Linux User.
  \item Experience using standard office software as well as LaTeX.
\end{itemize}

%horizontal line
\vskip 2pt
\hrule
{\large\bf WORK EXPERIENCE}

{\bf Oracle,} Endeca Server Team, {\sl Boston, MA} \hfill Apr-Aug 2013 \\
{\sl Software Developer}
\begin{itemize}
  \item Worked on performance and scaling team of an analytical database, coding in C++.
  \item Increased query performance by up to 10\% by finding and fixing a bug in cache eviction algorithm.
\end{itemize}

{\bf Autodesk,} Alias Team, {\sl Toronto, ON} \hfill Aug-Dec 2012 \\
{\sl Software Developer}
\begin{itemize}
  \item Developed software for a 3D modelling program.
  \item Completely redesigned the printing work-flow, integrating Qt into a product that did not previously use it.
\end{itemize}

{\bf Avvasi Inc,} Packet Processing Team, {\sl Waterloo, ON} \hfill Jan-Apr 2012 \\
{\sl Software Developer}
\begin{itemize}
  \item Worked on product to analyze and improve video streaming over a large-scale network.
  \item Ported RTMP and RTSP parsers from an older product to a newer one using C++.
\end{itemize}

{\bf Netkeepers} {\sl Markham, ON} \hfill May-Aug 2011 \\
{\sl Support Technician}
\begin{itemize}
  \item Assisted customers remotely to troubleshoot computer-related issues.
\end{itemize}

{\bf University of Waterloo} {\sl Waterloo, ON} \hfill Jan-Apr, Sept-Dec 2010 \\
{\sl Teaching Assistant and Lab Developer (GENE 121)}
\begin{itemize}
  \item Helped create labs using LEGO NXT and Arduino robots newly added to the course.
  \item Ran extra-help sessions before final exams; created a practice final for students.
\end{itemize}

%horizontal line
\vskip 2pt
\hrule
{\large\bf EDUCATION}

{\bf Candidate for Bachelor of Applied Science} \hfill 2009 - 2014 (Expected) \\
Mechatronics Engineering \hfill University of Waterloo, ON

{\bf Fourth Year Design Project} - \href{http://www.casesensitive.ca}{www.casesensitive.ca} \hfill Sept 2013 - Apr 2014
\begin{itemize}
  \item Designing a ``smart'' suitcase that tracks its position, detects mishandling, and weighs itself; reporting this information to a smart-phone.
  \item Software lead in a team of four.
  \item Coding in C++ and Java, using an Arduino and creating an app on Android.
\end{itemize}

%horizontal line
\vskip 2pt
\hrule
{\large\bf INTERESTS}
\begin{itemize}
  \item Member of University of Waterloo Engineering Society
  \begin{itemize}
    \item Volunteered at resume critiques for first year students.
    \item Volunteered as an orientation week leader.
  \end{itemize}
\end{itemize}

\end{document}
